A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-06-22 03_Prep_data.Rmd
commas with "which"

The experiment summaries report either standard deviation, least square differences or no error term (`NA`). 
First we will convert LSD and standard deviation to sample variance.
Then we will impute variances for the trials which did not report any form of variance (`NA`).

@@

We see here that the sample variance generally decreases or has no association with the grain yield.
This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares which defines between trial variation and is the more generic error term.

@@

Let's tidy up the data set into a data frame of only the variables which are required for the analysis.

@@

```{r clustered_fungicide_applications}
source("R/slimming_PM_dat.R") # see R script for the code which reduces the data.

@@

Earlier we noted there were different doses of propiconazole which might influence our analysis.
Let's check this by comparing a linear mixed effect model including and excluding dose.
We already have a factor breaking down the dose in the `trial` variable.
Let's make a new one without dose.

@@

We may want to consider row spacing in the trials, However one of the locations has `NA` as the row spacing. 
For now let's assign the most used row spacing of 0.33 m.

>>>>

The experiment summaries report either standard deviation, least square differences or no error term (`NA`). 
First we will convert LSD and standard deviation to sample variance.
Then we will impute variances for the trials, which did not report any form of variance (`NA`).

@@

We see here that the sample variance generally decreases or has no association with the grain yield.
This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares, which defines between trial variation and is the more generic error term.

@@

Let's tidy up the data set into a data frame of only the variables, which are required for the analysis.

@@

```{r clustered_fungicide_applications}
source("R/slimming_PM_dat.R") # see R script for the code, which reduces the data.

@@

Earlier we noted there were different doses of propiconazole, which might influence our analysis.
Let's check this by comparing a linear mixed effect model including and excluding dose.
We already have a factor breaking down the dose in the `trial` variable.
Let's make a new one without dose.

@@

We may want to consider row spacing in the trials.
However one of the locations has `NA` as the row spacing.
For now let's assign the most used row spacing of 0.33 m.
